\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-05 analysis/paper/paper.Rmd
overall accuracy table

df <- data.frame(oa = c("species", "genus", 382, 384),
                 species = c(94, 1220, 1733, 2922),
                 genus = )

>>>>

df <- data.frame(oa = c("Out-of-bag (OOB)", "Independent validation"),
                 species = c(54.6, 54.9),
                 genus = c(60.5, 60.0))

knitr::kable(x = df, 
             # set column names
             col.names = c("Overall Accuracy (%):",
                           "Species Classification",
                           "Genus Classification"),
             # center align text in the columns
             align = c("c", "c", "c"),
             format = "simple")
```
